---
title: "Hyunjin GO analysis"
author: "Trent"
date: "5/13/2021"
output: html_document
---

Use Hyunjin's code to set up the pathwayAnalysis_CP function:
```{r}
# ******************************************************************************************
# Pathway Analysis with clusterProfiler package
# Input: geneList     = a vector of gene Entrez IDs for pathway analysis [numeric or character]
#        org          = organism that will be used in the analysis ["human" or "mouse"]
#                       should be either "human" or "mouse"
#        database     = pathway analysis database (KEGG or GO) ["KEGG" or "GO"]
#        title        = title of the pathway figure [character]
#        pv_threshold = pathway analysis p-value threshold (not DE analysis threshold) [numeric]
#        displayNum   = the number of pathways that will be displayed [numeric]
#                       (If there are many significant pathways show the few top pathways)
#        imgPrint     = print a plot of pathway analysis [TRUE/FALSE]
#        dir          = file directory path of the output pathway figure [character]
#
# Output: Pathway analysis results in figure - using KEGG and GO pathways
#         The x-axis represents the number of DE genes in the pathway
#         The y-axis represents pathway names
#         The color of a bar indicates adjusted p-value from the pathway analysis
#         For Pathview Result, all colored genes are found DE genes in the pathway,
#         and the color indicates log2(fold change) of the DE gene from DE analysis
# ******************************************************************************************
pathwayAnalysis_CP <- function(geneList,
                               org,
                               database,
                               title="Pathway_Results",
                               pv_threshold=0.05,
                               displayNum=Inf,
                               imgPrint=TRUE,
                               dir="./") {
 
  ### load library
  if(!require(clusterProfiler, quietly = TRUE)) {
    if (!requireNamespace("BiocManager", quietly = TRUE))
      install.packages("BiocManager")
    BiocManager::install("clusterProfiler")
    require(clusterProfiler, quietly = TRUE)
  }
  if(!require(ggplot2)) {
    install.packages("ggplot2")
    library(ggplot2)
  }
 
 
  ### collect gene list (Entrez IDs)
  geneList <- geneList[which(!is.na(geneList))]
 
  if(!is.null(geneList)) {
    ### make an empty list
    p <- list()
   
    if(database == "KEGG") {
      ### KEGG Pathway
      kegg_enrich <- enrichKEGG(gene = geneList, organism = org, pvalueCutoff = pv_threshold)
     
      if(is.null(kegg_enrich)) {
        writeLines("KEGG Result does not exist")
        return(NULL)
      } else {
        kegg_enrich@result <- kegg_enrich@result[which(kegg_enrich@result$p.adjust < pv_threshold),]
       
        if(imgPrint == TRUE) {
          if((displayNum == Inf) || (nrow(kegg_enrich@result) <= displayNum)) {
            result <- kegg_enrich@result
            description <- kegg_enrich@result$Description
          } else {
            result <- kegg_enrich@result[1:displayNum,]
            description <- kegg_enrich@result$Description[1:displayNum]
          }
         
          if(nrow(kegg_enrich) > 0) {
            p[[1]] <- ggplot(result, aes(x=Description, y=Count)) + labs(x="", y="Gene Counts") +
              theme_classic(base_size = 50) + geom_bar(aes(fill = p.adjust), stat="identity") + coord_flip() +
              scale_x_discrete(limits = rev(description)) +
              guides(fill = guide_colorbar(ticks=FALSE, title="P.Val", barheight=10)) +
              ggtitle(paste0("KEGG ", title)) +
              theme(axis.text = element_text(size = 50))
           
            png(paste0(dir, "kegg_", title, "_CB.png"), width = 2200, height = 1000)
            print(p[[1]])
            dev.off()
          } else {
            writeLines("KEGG Result does not exist")
          }
        }
       
        return(kegg_enrich@result)
      }
    } else if(database == "GO") {
      ### GO Pathway
      if(org == "human") {
        go_enrich <- enrichGO(gene = geneList, OrgDb = 'org.Hs.eg.db', readable = T, ont = "BP", pvalueCutoff = pv_threshold)
      } else if(org == "mouse") {
        go_enrich <- enrichGO(gene = geneList, OrgDb = 'org.Mm.eg.db', readable = T, ont = "BP", pvalueCutoff = pv_threshold)
      } else {
        go_enrich <- NULL
        writeLines(paste("Unknown org variable:", org))
      }
     
      if(is.null(go_enrich)) {
        writeLines("GO Result does not exist")
        return(NULL)
      } else {
        go_enrich@result <- go_enrich@result[which(go_enrich@result$p.adjust < pv_threshold),]
       
        if(imgPrint == TRUE) {
          if((displayNum == Inf) || (nrow(go_enrich@result) <= displayNum)) {
            result <- go_enrich@result
            description <- go_enrich@result$Description
          } else {
            result <- go_enrich@result[1:displayNum,]
            description <- go_enrich@result$Description[1:displayNum]
          }
         
          if(nrow(go_enrich) > 0) {
            p[[2]] <- ggplot(result, aes(x=Description, y=Count)) + labs(x="", y="Gene Counts") +
              theme_classic(base_size = 50) + geom_bar(aes(fill = p.adjust), stat="identity") + coord_flip() +
              scale_x_discrete(limits = rev(description)) +
              guides(fill = guide_colorbar(ticks=FALSE, title="P.Val", barheight=10)) +
              ggtitle(paste0("GO ", title)) +
              theme(axis.text = element_text(size = 50))
           
            png(paste0(dir, "go_", title, "_CB.png"), width = 2200, height = 1000)
            print(p[[2]])
            dev.off()
          } else {
            writeLines("GO Result does not exist")
          }
        }
       
        return(go_enrich@result)
      }
    } else {
      stop("database prameter should be \"GO\" or \"KEGG\"")
    }
  } else {
    writeLines("geneList = NULL")
  }
}

if(!require(org.Mm.eg.db, quietly = TRUE)) {
  if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
  BiocManager::install("org.Mm.eg.db")
  require(org.Mm.eg.db, quietly = TRUE)
}
```
Take all of the gene lists required and turn them into vectors that can be used (the gene lists I have are gene symbols, so need them to be converted to Entrez Gene IDs):
```{r}
###Load all data333
library(readxl)
GO_data <- read_excel("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/GO_genes.xlsx")

###Convert excel data to vectors###

L0<-GO_data$L0
L2<-GO_data$L2
L3<-GO_data$L3
L5<-GO_data$L5
L6<-GO_data$L6
L7<-GO_data$L7
M0<-GO_data$M0
M2<-GO_data$M2
M3<-GO_data$M3
BML16<-GO_data$BML16
FLL16<-GO_data$FLL16
BMLP0<-GO_data$BMLP0
FLLP0<-GO_data$FLLP0
BMT16<-GO_data$BMT16
BMM16<-GO_data$BMM16
FLEM16<-GO_data$FLEM16

###Convert the gene symbols to Entrez Gene IDs###

L0 <- mapIds(org.Mm.eg.db,
L0,
"ENTREZID", "SYMBOL")
L0 <- L0[!is.na(L0)]

L2 <- mapIds(org.Mm.eg.db,
L2,
"ENTREZID", "SYMBOL")
L2 <- L2[!is.na(L2)]

L3 <- mapIds(org.Mm.eg.db,
L3,
"ENTREZID", "SYMBOL")
L3 <- L3[!is.na(L3)]

L5 <- mapIds(org.Mm.eg.db,
L5,
"ENTREZID", "SYMBOL")
L5 <- L5[!is.na(L5)]

L6 <- mapIds(org.Mm.eg.db,
L6,
"ENTREZID", "SYMBOL")
L6 <- L6[!is.na(L6)]

L7 <- mapIds(org.Mm.eg.db,
L7,
"ENTREZID", "SYMBOL")
L7 <- L7[!is.na(L7)]

M0 <- mapIds(org.Mm.eg.db,
M0,
"ENTREZID", "SYMBOL")
M0 <- M0[!is.na(M0)]

M2 <- mapIds(org.Mm.eg.db,
M2,
"ENTREZID", "SYMBOL")
M2 <- M2[!is.na(M2)]

M3 <- mapIds(org.Mm.eg.db,
M3,
"ENTREZID", "SYMBOL")
M3 <- M3[!is.na(M3)]

BML16 <- mapIds(org.Mm.eg.db,
BML16,
"ENTREZID", "SYMBOL")
BML16 <- BML16[!is.na(BML16)]

FLL16 <- mapIds(org.Mm.eg.db,
FLL16,
"ENTREZID", "SYMBOL")
FLL16 <- FLL16[!is.na(FLL16)]

BMLP0 <- mapIds(org.Mm.eg.db,
BMLP0,
"ENTREZID", "SYMBOL")
BMLP0 <- BMLP0[!is.na(BMLP0)]

FLLP0 <- mapIds(org.Mm.eg.db,
FLLP0,
"ENTREZID", "SYMBOL")
FLLP0 <- FLLP0[!is.na(FLLP0)]

BMT16 <- mapIds(org.Mm.eg.db,
BMT16,
"ENTREZID", "SYMBOL")
BMT16 <- BMT16[!is.na(BMT16)]

BMM16 <- mapIds(org.Mm.eg.db,
BMM16,
"ENTREZID", "SYMBOL")
BMM16 <- BMM16[!is.na(BMM16)]

FLEM16 <- mapIds(org.Mm.eg.db,
FLEM16,
"ENTREZID", "SYMBOL")
FLEM16 <- FLEM16[!is.na(FLEM16)]

```
Now convert each to an excel workbook:
```{r}
L0 <-unlist(L0)
write.csv(L0, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L0.csv")
L2 <-unlist(L2)
write.csv(L2, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L2.csv")
L3 <-unlist(L3)
write.csv(L3, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L3.csv")
L5 <-unlist(L5)
write.csv(L5, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L5.csv")
L6 <-unlist(L6)
write.csv(L6, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L6.csv")
L7 <-unlist(L7)
write.csv(L7, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L7.csv")
M0 <-unlist(M0)
write.csv(M0, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/M0.csv")
M2 <-unlist(M2)
write.csv(M2, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/M2.csv")
M3 <-unlist(M3)
write.csv(M3, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/M3.csv")
BML16 <-unlist(BML16)
write.csv(BML16, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/BML16.csv")
FLL16 <-unlist(FLL16)
write.csv(FLL16, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/FLL16.csv")
BMLP0 <-unlist(BMLP0)
write.csv(BMLP0, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/BMLP0.csv")
FLLP0 <-unlist(FLLP0)
write.csv(FLLP0, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/FLLP0.csv")
BMT16 <-unlist(BMT16)
write.csv(BMT16, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/BMT16.csv")
BMM16 <-unlist(BMM16)
write.csv(BMM16, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/BMM16.csv")
FLEM16 <-unlist(FLEM16)
write.csv(L0, "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/FLEM16.csv")

```
Now, import each as a dataframe:
```{r}
L0_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L0.csv", header = FALSE)
L2_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L2.csv", header = FALSE)
L3_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L3.csv", header = FALSE)
L5_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L5.csv", header = FALSE)
L6_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L6.csv", header = FALSE)
L7_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L7.csv", header = FALSE)
M0_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/M0.csv", header = FALSE)
M2_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/M2.csv", header = FALSE)
M3_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/M3.csv", header = FALSE)
BML16_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/BML16.csv", header = FALSE)
FLL16_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/FLL16.csv", header = FALSE)
BMLP0_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/BMLP0.csv", header = FALSE)
FLLP0_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/FLLP0.csv", header = FALSE)
BMT16_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/BMT16.csv", header = FALSE)
BMM16_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/BMM16.csv", header = FALSE)
FLEM16_IDs <- read.csv("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/FLEM16.csv", header = FALSE)
```
Now convert each of the gene ID columns into vectors:
```{r}
L0_IDS <- as.vector(L0_IDs[,1])
L2_IDS <- as.vector(L2_IDs[,1])
L3_IDS <- as.vector(L3_IDs[,1])
L5_IDS <- as.vector(L5_IDs[,1])
L6_IDS <- as.vector(L6_IDs[,1])
L7_IDS <- as.vector(L7_IDs[,1])
M0_IDS <- as.vector(M0_IDs[,1])
M2_IDS <- as.vector(M2_IDs[,1])
M3_IDS <- as.vector(M3_IDs[,1])
BML16_IDS <- as.vector(BML16_IDs[,1])
FLL16_IDS <- as.vector(FLL16_IDs[,1])
BMLP0_IDS <- as.vector(BMLP0_IDs[,1])
FLLP0_IDS <- as.vector(FLLP0_IDs[,1])
BMT16_IDS <- as.vector(BMT16_IDs[,1])
BMM16_IDS <- as.vector(BMM16_IDs[,1])
FLEM16_IDS <- as.vector(FLEM16_IDs[,1])

```
Now attempt to run Hyunjin's program with each vector:
```{r}
L0_GO <- pathwayAnalysis_CP(geneList = L0_IDS, org = "mouse", database = "GO", title = "L0_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(L0_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L0_GO_results.csv", row.names = FALSE)

L2_GO <- pathwayAnalysis_CP(geneList = L2_IDS, org = "mouse", database = "GO", title = "L2_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(L2_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L2_GO_results.csv", row.names = FALSE)

L3_GO <- pathwayAnalysis_CP(geneList = L3_IDS, org = "mouse", database = "GO", title = "L3_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(L3_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L3_GO_results.csv", row.names = FALSE)

L5_GO <- pathwayAnalysis_CP(geneList = L5_IDS, org = "mouse", database = "GO", title = "L5_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(L5_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L5_GO_results.csv", row.names = FALSE)

L6_GO <- pathwayAnalysis_CP(geneList = L6_IDS, org = "mouse", database = "GO", title = "L6_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(L6_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L6_GO_results.csv", row.names = FALSE)

L7_GO <- pathwayAnalysis_CP(geneList = L7_IDS, org = "mouse", database = "GO", title = "L7_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(L7_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/L7_GO_results.csv", row.names = FALSE)

M0_GO <- pathwayAnalysis_CP(geneList = M0_IDS, org = "mouse", database = "GO", title = "M0_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(M0_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/M0_GO_results.csv", row.names = FALSE)

M2_GO <- pathwayAnalysis_CP(geneList = M2_IDS, org = "mouse", database = "GO", title = "M2_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(M2_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/M2_GO_results.csv", row.names = FALSE)

M3_GO <- pathwayAnalysis_CP(geneList = M3_IDS, org = "mouse", database = "GO", title = "M3_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(M3_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/M3_GO_results.csv", row.names = FALSE)

BML16_GO <- pathwayAnalysis_CP(geneList = BML16_IDS, org = "mouse", database = "GO", title = "BML16_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(BML16_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/BML16_GO_results.csv", row.names = FALSE)

FLL16_GO <- pathwayAnalysis_CP(geneList = FLL16_IDS, org = "mouse", database = "GO", title = "FLL16_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(FLL16_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/FLL16_GO_results.csv", row.names = FALSE)

BMLP0_GO <- pathwayAnalysis_CP(geneList = BMLP0_IDS, org = "mouse", database = "GO", title = "BMLP0_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(BMLP0_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/BMLP0_GO_results.csv", row.names = FALSE)

FLLP0_GO <- pathwayAnalysis_CP(geneList = FLLP0_IDS, org = "mouse", database = "GO", title = "FLLP0_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(FLLP0_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/FLLP0_GO_results.csv", row.names = FALSE)

BMT16_GO <- pathwayAnalysis_CP(geneList = BMT16_IDS, org = "mouse", database = "GO", title = "BMT16_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(BMT16_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/BMT16_GO_results.csv", row.names = FALSE)

BMM16_GO <- pathwayAnalysis_CP(geneList = BMM16_IDS, org = "mouse", database = "GO", title = "BMM16_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(BMM16_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/BMM16_GO_results.csv", row.names = FALSE)

FLEM16_GO <- pathwayAnalysis_CP(geneList = FLEM16_IDS, org = "mouse", database = "GO", title = "FLEM16_GO_Terms", displayNum = 10, imgPrint = TRUE, dir = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/") 
write.csv(FLEM16_GO, file = "C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Intrinsic/FLEM16_GO_results.csv", row.names = FALSE)


```
