---
title: "20201116 Stroma Integration TDH"
author: "Trent"
date: "11/16/2020"
output: html_document 
---
```{r}
library(Seurat)
load("C:/Users/thall/Desktop/singlecell2/Stroma/StromaE16_regress2")
load("C:/Users/thall/Desktop/singlecell2/Stroma/StromaE18_regress2")
load("C:/Users/thall/Desktop/singlecell2/Stroma/StromaP0_regress2")
load("C:/Users/thall/Desktop/singlecell2/Stroma/StromaADULT_regress2")
```
Add in developmental time to identities
```{r}
Idents(StromaE16_regress2) <- paste(Idents(StromaE16_regress2), "E16", sep="_")
Idents(StromaE18_regress2) <- paste(Idents(StromaE18_regress2), "E18", sep="_")
Idents(StromaP0_regress2) <- paste(Idents(StromaP0_regress2), "P0", sep="_")
Idents(StromaADULT_regress2) <- paste(Idents(StromaADULT_regress2), "ADULT", sep="_")
```
Double check identities
```{r}
summary(Idents(StromaE16_regress2))
summary(Idents(StromaE18_regress2))
summary(Idents(StromaP0_regress2))
summary(Idents(StromaADULT_regress2))
```
Cell cycle regression needed?
```{r}
FeaturePlot(StromaE16_regress2, features = "Top2a")
FeaturePlot(StromaE18_regress2, features = "Top2a")
FeaturePlot(StromaP0_regress2, features = "Top2a")
FeaturePlot(StromaADULT_regress2, features = "Top2a")
```
Merge objects together 
```{r}
combined <- merge(x = StromaE16_regress2, y = list(StromaE18_regress2,StromaP0_regress2,StromaADULT_regress2), add.cell.ids = c("StromaE16","StromaE18", "StromaP0", "StromaADULT"))
tail(x = combined@meta.data)
summary(Idents(combined))
table(combined@meta.data$Time)
DefaultAssay(combined) <- "RNA"
combined <- FindVariableFeatures(combined, selection.method = "vst", nfeatures = 2000)
top10 <- head(VariableFeatures(combined), 10)
top10
all.genes <- rownames(combined)
combined <- ScaleData(combined, features = all.genes)
combined <- RunPCA(combined, features = VariableFeatures(object = combined))
ElbowPlot(combined)
combined <- RunUMAP(combined, dims = 1:20)
DimPlot(combined, reduction = "umap")
save(combined, file = "C:/Users/thall/Desktop/singlecell2/Stroma/Stroma_combined.Robj")
```
If you ever return, just load the "Stroma_combined.Robj" object. Go through all cluster combinations and identify overlapping populations. Start with the clusters I've annotated as "C".
```{r}
```


```{r}
Chondro <- subset(x = combined, idents = c("C-1_ADULT", "C-1_E16", "C-1_E18", "C-2_ADULT", "C-2_E16", "C-2_E18", "C-3_ADULT", "C-3_E16", "C-3_E18", "C-4_E16", "C-4_E18", "C-5_E16", "C-5_E18"))
```


```{r}
DimPlot(Chondro, reduction = "umap", cols = c("purple","magenta","red","pink","green" ,"darkgreen", "blue","cyan", "black", "brown","gold","orange","yellow", pt.size = 1))
DimPlot(Chondro, reduction = "umap", cols = c("red","blue","yellow","green",rep("grey",9)))
DimPlot(Chondro, reduction = "umap", cols = c("red",rep("grey",3),"blue","yellow","green",rep("grey",6)))
DimPlot(Chondro, reduction = "umap", cols = c("red",rep("grey",6),"blue","yellow","green",rep("grey",3)))
DimPlot(Chondro, reduction = "umap", cols = c("red",rep("grey",9),"blue","yellow","green"))
DimPlot(Chondro, reduction = "umap", cols = c("grey","red",rep("grey",2),"blue","yellow","green",rep("grey",6)))
DimPlot(Chondro, reduction = "umap", cols = c("grey","red",rep("grey",5),"blue","yellow","green",rep("grey",3)))
DimPlot(Chondro, reduction = "umap", cols = c("grey","red",rep("grey",8),"blue","yellow","green"))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",2),"red","grey","blue","yellow","green",rep("grey",7)))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",2),"red",rep("grey",4),"blue","yellow","green",rep("grey",3)))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",2),"red",rep("grey",7),"blue","yellow","green"))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",3),"red","blue","yellow","green",rep("grey",6)))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",3),"red",rep("grey",3),"blue","yellow","green",rep("grey",3)))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",3),"red",rep("grey",6),"blue","yellow","green"))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",4),"red",rep("grey",2),"blue","yellow","green",rep("grey",3)))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",4),"red",rep("grey",5),"blue","yellow","green"))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",5),"red",rep("grey",1),"blue","yellow","green",rep("grey",3)))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",5),"red",rep("grey",4),"blue","yellow","green"))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",6),"red","blue","yellow","green",rep("grey",3)))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",6),"red",rep("grey",3),"blue","yellow","green"))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",7),"red", rep("grey",2),"blue","yellow","green"))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",8),"red", rep("grey",1),"blue","yellow","green"))
DimPlot(Chondro, reduction = "umap", cols = c(rep("grey",9),"red", "blue","yellow","green"))
```
Next, the Fibroblast populations
```{r}
Fibro <- subset(x = combined, idents = c("F-1_ADULT", "F-1_E16", "F-1_E18", "F-1_P0", "F-2_ADULT", "F-2_E16", "F-2_E18", "F-2_P0", "F-3_ADULT", "F-3_E16", "F-3_P0", "F-4_ADULT", "F-4_E16", "F-4_P0", "F-5_ADULT", "F-5_E16", "F-5_P0", "F-6_ADULT", "F-6_E16"))
DimPlot(Fibro, reduction = "umap", cols = c("red","blue","yellow","green",rep("grey",15)))
DimPlot(Fibro, reduction = "umap", cols = c("red",rep("grey",3),"blue","yellow","green",rep("grey",12)))
DimPlot(Fibro, reduction = "umap", cols = c("red",rep("grey",6),"blue","yellow","green",rep("grey",9)))
DimPlot(Fibro, reduction = "umap", cols = c("red",rep("grey",9),"blue","yellow","green",rep("grey",6)))
DimPlot(Fibro, reduction = "umap", cols = c("red",rep("grey",12),"blue","yellow","green",rep("grey",3)))
DimPlot(Fibro, reduction = "umap", cols = c("red",rep("grey",15),"blue","yellow","green"))
DimPlot(Fibro, reduction = "umap", cols = c("grey","red",rep("grey",2),"blue","yellow","green",rep("grey",12)))
DimPlot(Fibro, reduction = "umap", cols = c("grey","red",rep("grey",5),"blue","yellow","green",rep("grey",9)))
DimPlot(Fibro, reduction = "umap", cols = c("grey","red",rep("grey",8),"blue","yellow","green",rep("grey",6)))
DimPlot(Fibro, reduction = "umap", cols = c("grey","red",rep("grey",11),"blue","yellow","green",rep("grey",3)))
DimPlot(Fibro, reduction = "umap", cols = c("grey","red",rep("grey",14),"blue","yellow","green"))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",2),"red","grey","blue","yellow","green",rep("grey",12)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",2),"red",rep("grey",4),"blue","yellow","green",rep("grey",9)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",2),"red",rep("grey",7),"blue","yellow","green",rep("grey",6)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",2),"red",rep("grey",10),"blue","yellow","green",rep("grey",3)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",2),"red",rep("grey",13),"blue","yellow","green"))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",3),"red",rep("grey",3),"blue","yellow","green",rep("grey",9)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",3),"red",rep("grey",6),"blue","yellow","green",rep("grey",6)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",3),"red",rep("grey",9),"blue","yellow","green",rep("grey",3)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",3),"red",rep("grey",12),"blue","yellow","green"))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",5),"red",rep("grey",1),"blue","yellow","green",rep("grey",9)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",5),"red",rep("grey",4),"blue","yellow","green",rep("grey",6)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",5),"red",rep("grey",7),"blue","yellow","green",rep("grey",3)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",5),"red",rep("grey",10),"blue","yellow","green"))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",6),"red","blue","yellow","green",rep("grey",9)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",6),"red",rep("grey",3),"blue","yellow","green",rep("grey",6)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",6),"red",rep("grey",6),"blue","yellow","green",rep("grey",3)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",6),"red",rep("grey",9),"blue","yellow","green"))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",7),"red",rep("grey",2),"blue","yellow","green",rep("grey",6)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",7),"red",rep("grey",5),"blue","yellow","green",rep("grey",3)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",7),"red",rep("grey",8),"blue","yellow","green"))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",9),"red",rep("grey",0),"blue","yellow","green",rep("grey",6)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",9),"red",rep("grey",3),"blue","yellow","green",rep("grey",3)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",9),"red",rep("grey",6),"blue","yellow","green"))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",10),"red",rep("grey",2),"blue","yellow","green",rep("grey",3)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",10),"red",rep("grey",5),"blue","yellow","green"))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",12),"red",rep("grey",0),"blue","yellow","green",rep("grey",3)))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",12),"red",rep("grey",3),"blue","yellow","green"))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",13),"red",rep("grey",2),"blue","yellow","green"))
DimPlot(Fibro, reduction = "umap", cols = c(rep("grey",15),"red",rep("grey",0),"blue","yellow","green"))
```
Next, the Chondro/Fibro populations
```{r}
Chondro_Fibro <- subset(x = combined, idents = c("C/F-1_E18", "C/F-1_P0", "C/F-2_E18", "C/F-2_P0", "C/F-3_E18", "C/F-3_P0", "C/F-4_E18", "C/F-4_P0", "C/F-5_P0", "C/F-6_P0", "C/F-7_P0"))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c("red","blue","green",rep("grey",8)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c("red",rep("grey",2),"blue","green",rep("grey",6)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c("red",rep("grey",4),"blue","green",rep("grey",4)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c("red",rep("grey",6),"blue","green",rep("grey",2)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c("red",rep("grey",8),"blue","green",rep("grey",0)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c("grey","red",rep("grey",1),"blue","green",rep("grey",6)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c("grey","red",rep("grey",3),"blue","green",rep("grey",4)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c("grey","red",rep("grey",5),"blue","green",rep("grey",2)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c("grey","red",rep("grey",7),"blue","green",rep("grey",0)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",2),"red",rep("grey",0),"blue","green",rep("grey",6)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",2),"red",rep("grey",2),"blue","green",rep("grey",4)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",2),"red",rep("grey",4),"blue","green",rep("grey",2)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",2),"red",rep("grey",6),"blue","green",rep("grey",0)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",3),"red",rep("grey",1),"blue","green",rep("grey",4)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",3),"red",rep("grey",3),"blue","green",rep("grey",2)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",3),"red",rep("grey",5),"blue","green",rep("grey",0)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",4),"red",rep("grey",0),"blue","green",rep("grey",4)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",4),"red",rep("grey",2),"blue","green",rep("grey",2)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",4),"red",rep("grey",4),"blue","green",rep("grey",0)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",5),"red",rep("grey",1),"blue","green",rep("grey",2)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",5),"red",rep("grey",3),"blue","green",rep("grey",0)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",6),"red",rep("grey",0),"blue","green",rep("grey",2)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",6),"red",rep("grey",2),"blue","green",rep("grey",0)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",7),"red",rep("grey",1),"blue","green",rep("grey",0)))
DimPlot(Chondro_Fibro, reduction = "umap", cols = c(rep("grey",8),"red",rep("grey",0),"blue","green",rep("grey",0)))
```
Now subset all of the "C", "F," or "C/F" that appear to have overlap to better visualize the overlap.
```{r}
Chondro_refined <- subset(x = combined, idents = c("C-1_E16", "C-1_E18","C-2_E16","C-2_E18", "C-3_E16", "C-3_E18", "C-4_E18", "C-5_E16", "C-5_E18"))
DimPlot(Chondro_refined, reduction = "umap", cols = c("purple","magenta","red","pink","green" ,"darkgreen", "blue","cyan", "black", pt.size = 1))
Chondro_refined_2 <- subset(x = combined, idents = c("C-1_E16", "C-1_E18"))
DimPlot(Chondro_refined_2, reduction = "umap", cols = c("red","blue"))
Chondro_refined_3 <- subset(x = combined, idents = c("C-2_E16", "C-5_E18"))
DimPlot(Chondro_refined_3, reduction = "umap", cols = c("red","blue"))
Chondro_refined_4 <- subset(x = combined, idents = c("C-2_E18", "C-3_E16", "C-3_E18"))
DimPlot(Chondro_refined_4, reduction = "umap", cols = c("red","blue","green"))
Chondro_refined_5 <- subset(x = combined, idents = c("C-2_E18", "C-3_E16"))
DimPlot(Chondro_refined_5, reduction = "umap", cols = c("red","blue"))
Chondro_refined_6 <- subset(x = combined, idents = c("C-2_E18", "C-3_E18"))
DimPlot(Chondro_refined_6, reduction = "umap", cols = c("red","blue"))
Chondro_refined_7 <- subset(x = combined, idents = c("C-3_E16", "C-3_E18"))
DimPlot(Chondro_refined_7, reduction = "umap", cols = c("red","blue"))
Chondro_refined_8 <- subset(x = combined, idents = c("C-4_E18", "C-5_E16"))
DimPlot(Chondro_refined_8, reduction = "umap", cols = c("red","blue"))
Fibro_refined <- subset(x = combined, idents = c("F-1_E16", "F-1_E18", "F-1_P0", "F-2_E18", "F-3_E16","F-3_P0","F-4_P0","F-5_P0","F-6_E16"))
DimPlot(Fibro_refined, reduction = "umap", cols = c("purple","magenta","red","pink","green" ,"darkgreen", "blue","cyan", "black", pt.size = 1))
Fibro_refined_2 <- subset(x = combined, idents = c("F-1_E16", "F-1_E18", "F-5_P0"))
DimPlot(Fibro_refined_2, reduction = "umap", cols = c("red","blue","green"))
Fibro_refined_3 <- subset(x = combined, idents = c("F-1_E16", "F-1_E18"))
DimPlot(Fibro_refined_3, reduction = "umap", cols = c("red","blue"))
Fibro_refined_4 <- subset(x = combined, idents = c("F-1_E16", "F-5_P0"))
DimPlot(Fibro_refined_4, reduction = "umap", cols = c("red","blue"))
Fibro_refined_5 <- subset(x = combined, idents = c("F-1_E18", "F-5_P0"))
DimPlot(Fibro_refined_5, reduction = "umap", cols = c("red","blue"))
Fibro_refined_6 <- subset(x = combined, idents = c("F-1_E18", "F-3_P0"))
DimPlot(Fibro_refined_6, reduction = "umap", cols = c("red","blue"))
Fibro_refined_7 <- subset(x = combined, idents = c("F-1_P0", "F-2_E18", "F-3_E16"))
DimPlot(Fibro_refined_7, reduction = "umap", cols = c("red","blue","green"))
Fibro_refined_8 <- subset(x = combined, idents = c("F-1_P0", "F-2_E18"))
Fibro_refined_9 <- subset(x = combined, idents = c("F-1_P0", "F-3_E16"))
Fibro_refined_10 <- subset(x = combined, idents = c("F-2_E18", "F-3_E16"))
DimPlot(Fibro_refined_8, reduction = "umap", cols = c("red","blue","green"))
DimPlot(Fibro_refined_9, reduction = "umap", cols = c("red","blue","green"))
DimPlot(Fibro_refined_10, reduction = "umap", cols = c("red","blue","green"))
Fibro_refined_11 <- subset(x = combined, idents = c("F-2_E18", "F-3_E16","F-6_E16"))
DimPlot(Fibro_refined_11, reduction = "umap", cols = c("red","blue","green"))
Fibro_refined_12 <- subset(x = combined, idents = c("F-2_E18", "F-6_E16"))
Fibro_refined_13 <- subset(x = combined, idents = c("F-3_E16", "F-6_E16"))
DimPlot(Fibro_refined_12, reduction = "umap", cols = c("red","blue","green"))
DimPlot(Fibro_refined_13, reduction = "umap", cols = c("red","blue","green"))
Fibro_refined_14 <- subset(x = combined, idents = c("F-3_E16", "F-5_P0"))
DimPlot(Fibro_refined_14, reduction = "umap", cols = c("red","blue","green"))
Fibro_refined_15 <- subset(x = combined, idents = c("F-4_P0", "F-5_E16"))
DimPlot(Fibro_refined_15, reduction = "umap", cols = c("red","blue","green"))
Chondro_Fibro_refined <- subset(x = combined, idents = c("C/F-1_E18", "C/F-2_E18", "C/F-2_P0", "C/F-3_E18","C/F-3_E18","C/F-3_P0","C/F-4_E18","C/F-4_P0","C/F-5_P0","C/F-6_P0","C/F-7_P0"))
DimPlot(Chondro_Fibro_refined, reduction = "umap", cols = c("purple","magenta","red","pink","green" ,"darkgreen", "blue","cyan", "black", "brown","gold"))
Chondro_Fibro_refined_2 <- subset(x = combined, idents = c("C/F-1_E18", "C/F-5_P0"))
DimPlot(Chondro_Fibro_refined_2, reduction = "umap", cols = c("red","blue"))
Chondro_Fibro_refined_3 <- subset(x = combined, idents = c("C/F-2_E18", "C/F-2_P0"))
Chondro_Fibro_refined_4 <- subset(x = combined, idents = c("C/F-2_E18", "C/F-3_P0"))
Chondro_Fibro_refined_5 <- subset(x = combined, idents = c("C/F-2_E18", "C/F-4_P0"))
DimPlot(Chondro_Fibro_refined_3, reduction = "umap", cols = c("red","blue"))
DimPlot(Chondro_Fibro_refined_4, reduction = "umap", cols = c("red","blue"))
DimPlot(Chondro_Fibro_refined_5, reduction = "umap", cols = c("red","blue"))
Chondro_Fibro_refined_6 <- subset(x = combined, idents = c("C/F-2_P0", "C/F-3_E18"))
Chondro_Fibro_refined_7 <- subset(x = combined, idents = c("C/F-2_P0", "C/F-4_E18"))
DimPlot(Chondro_Fibro_refined_6, reduction = "umap", cols = c("red","blue"))
DimPlot(Chondro_Fibro_refined_7, reduction = "umap", cols = c("red","blue"))
Chondro_Fibro_refined_8 <- subset(x = combined, idents = c("C/F-3_E18", "C/F-6_P0"))
Chondro_Fibro_refined_9 <- subset(x = combined, idents = c("C/F-3_E18", "C/F-7_P0"))
DimPlot(Chondro_Fibro_refined_8, reduction = "umap", cols = c("red","blue"))
DimPlot(Chondro_Fibro_refined_9, reduction = "umap", cols = c("red","blue"))
Chondro_Fibro_refined_10 <- subset(x = combined, idents = c("C/F-6_P0", "C/F-7_P0"))
DimPlot(Chondro_Fibro_refined_10, reduction = "umap", cols = c("red","blue"))
```
Are there any Chondro, Fibro, or C/F clusters that overlap?
```{r}
DimPlot(combined, reduction = "umap", cols = c("grey", rep("red",13), rep("blue",11),rep("grey",4),rep("green",19),rep("grey",18)))
```
Yes, let's just look at the Chondro, Fibro, and C/F populations and see if we can tease out what is happening.
```{r}
Chondro_Fibro_CF <- subset(x = combined, idents = c("C-1_ADULT", "C-1_E16", "C-1_E18", "C-2_ADULT", "C-2_E16", "C-2_E18", "C-3_ADULT", "C-3_E16", "C-3_E18", "C-4_E16", "C-4_E18", "C-5_E16", "C-5_E18","F-1_ADULT", "F-1_E16", "F-1_E18", "F-1_P0", "F-2_ADULT", "F-2_E16", "F-2_E18", "F-2_P0", "F-3_ADULT", "F-3_E16", "F-3_P0", "F-4_ADULT", "F-4_E16", "F-4_P0", "F-5_ADULT", "F-5_E16", "F-5_P0", "F-6_ADULT", "F-6_E16","C/F-1_E18", "C/F-1_P0", "C/F-2_E18", "C/F-2_P0", "C/F-3_E18", "C/F-3_P0", "C/F-4_E18", "C/F-4_P0", "C/F-5_P0", "C/F-6_P0", "C/F-7_P0"))
DimPlot(Chondro_Fibro_CF, reduction = "umap", label = TRUE)
```
The adult do not cluster with anything else, so let's get rid of it.
```{r}
```


```{r}
Chondro_Fibro_CF <- subset(x = combined, idents = c("C-1_E16", "C-1_E18", "C-2_E16", "C-2_E18", "C-3_E16", "C-3_E18", "C-4_E16", "C-4_E18", "C-5_E16", "C-5_E18", "F-1_E16", "F-1_E18", "F-1_P0","F-2_E16", "F-2_E18", "F-2_P0", "F-3_E16", "F-3_P0", "F-4_E16", "F-4_P0","F-5_E16", "F-5_P0", "F-6_E16","C/F-1_E18", "C/F-1_P0", "C/F-2_E18", "C/F-2_P0", "C/F-3_E18", "C/F-3_P0", "C/F-4_E18", "C/F-4_P0", "C/F-5_P0", "C/F-6_P0", "C/F-7_P0"))
```


```{r}
DimPlot(Chondro_Fibro_CF, reduction = "umap")
```
First, let's compare the perinatal C vs C/F, C vs F, and C/F vs F populations:
```{r}
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c("red", rep("grey",9),"blue","green","yellow",rep("grey",21)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c("red", rep("grey",12),"blue","green","yellow",rep("grey",18)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c("red", rep("grey",15),"blue","green","yellow",rep("grey",15)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c("red", rep("grey",18),"blue","green","yellow",rep("grey",12)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c("red", rep("grey",21),"blue","green","yellow",rep("grey",9)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c("red", rep("grey",24),"blue","green","yellow",rep("grey",6)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c("red", rep("grey",27),"blue","green","yellow",rep("grey",3)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c("red", rep("grey",30),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",1),"red", rep("grey",8),"blue","green","yellow",rep("grey",21)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",1),"red", rep("grey",11),"blue","green","yellow",rep("grey",18)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",1),"red", rep("grey",14),"blue","green","yellow",rep("grey",15)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",1),"red", rep("grey",17),"blue","green","yellow",rep("grey",12)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",1),"red", rep("grey",20),"blue","green","yellow",rep("grey",9)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",1),"red", rep("grey",23),"blue","green","yellow",rep("grey",6)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",1),"red", rep("grey",26),"blue","green","yellow",rep("grey",3)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",1),"red", rep("grey",29),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",2),"red", rep("grey",7),"blue","green","yellow",rep("grey",21)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",2),"red", rep("grey",10),"blue","green","yellow",rep("grey",18)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",2),"red", rep("grey",13),"blue","green","yellow",rep("grey",15)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",2),"red", rep("grey",16),"blue","green","yellow",rep("grey",12)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",2),"red", rep("grey",19),"blue","green","yellow",rep("grey",9)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",2),"red", rep("grey",22),"blue","green","yellow",rep("grey",6)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",2),"red", rep("grey",25),"blue","green","yellow",rep("grey",3)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",2),"red", rep("grey",28),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",3),"red", rep("grey",6),"blue","green","yellow",rep("grey",21)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",3),"red", rep("grey",9),"blue","green","yellow",rep("grey",18)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",3),"red", rep("grey",12),"blue","green","yellow",rep("grey",15)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",3),"red", rep("grey",15),"blue","green","yellow",rep("grey",12)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",3),"red", rep("grey",18),"blue","green","yellow",rep("grey",9)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",3),"red", rep("grey",21),"blue","green","yellow",rep("grey",6)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",3),"red", rep("grey",24),"blue","green","yellow",rep("grey",3)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",3),"red", rep("grey",27),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",4),"red", rep("grey",5),"blue","green","yellow",rep("grey",21)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",4),"red", rep("grey",8),"blue","green","yellow",rep("grey",18)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",4),"red", rep("grey",11),"blue","green","yellow",rep("grey",15)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",4),"red", rep("grey",14),"blue","green","yellow",rep("grey",12)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",4),"red", rep("grey",17),"blue","green","yellow",rep("grey",19)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",4),"red", rep("grey",20),"blue","green","yellow",rep("grey",6)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",4),"red", rep("grey",23),"blue","green","yellow",rep("grey",3)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",4),"red", rep("grey",26),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",5),"red", rep("grey",4),"blue","green","yellow",rep("grey",21)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",5),"red", rep("grey",7),"blue","green","yellow",rep("grey",18)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",5),"red", rep("grey",10),"blue","green","yellow",rep("grey",15)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",5),"red", rep("grey",13),"blue","green","yellow",rep("grey",12)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",5),"red", rep("grey",16),"blue","green","yellow",rep("grey",9)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",5),"red", rep("grey",19),"blue","green","yellow",rep("grey",6)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",5),"red", rep("grey",22),"blue","green","yellow",rep("grey",3)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",5),"red", rep("grey",25),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",6),"red", rep("grey",3),"blue","green","yellow",rep("grey",21)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",6),"red", rep("grey",6),"blue","green","yellow",rep("grey",18)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",6),"red", rep("grey",9),"blue","green","yellow",rep("grey",15)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",6),"red", rep("grey",12),"blue","green","yellow",rep("grey",12)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",6),"red", rep("grey",15),"blue","green","yellow",rep("grey",9)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",6),"red", rep("grey",18),"blue","green","yellow",rep("grey",6)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",6),"red", rep("grey",21),"blue","green","yellow",rep("grey",3)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",6),"red", rep("grey",24),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",7),"red", rep("grey",2),"blue","green","yellow",rep("grey",21)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",7),"red", rep("grey",5),"blue","green","yellow",rep("grey",18)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",7),"red", rep("grey",8),"blue","green","yellow",rep("grey",15)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",7),"red", rep("grey",11),"blue","green","yellow",rep("grey",12)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",7),"red", rep("grey",14),"blue","green","yellow",rep("grey",9)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",7),"red", rep("grey",17),"blue","green","yellow",rep("grey",6)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",7),"red", rep("grey",20),"blue","green","yellow",rep("grey",3)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",7),"red", rep("grey",23),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",8),"red", rep("grey",1),"blue","green","yellow",rep("grey",21)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",8),"red", rep("grey",4),"blue","green","yellow",rep("grey",18)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",8),"red", rep("grey",7),"blue","green","yellow",rep("grey",15)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",8),"red", rep("grey",10),"blue","green","yellow",rep("grey",12)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",8),"red", rep("grey",13),"blue","green","yellow",rep("grey",9)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",8),"red", rep("grey",16),"blue","green","yellow",rep("grey",6)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",8),"red", rep("grey",19),"blue","green","yellow",rep("grey",3)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",8),"red", rep("grey",22),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",9),"red", rep("grey",0),"blue","green","yellow",rep("grey",21)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",9),"red", rep("grey",3),"blue","green","yellow",rep("grey",18)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",9),"red", rep("grey",6),"blue","green","yellow",rep("grey",15)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",9),"red", rep("grey",9),"blue","green","yellow",rep("grey",12)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",9),"red", rep("grey",12),"blue","green","yellow",rep("grey",9)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",9),"red", rep("grey",15),"blue","green","yellow",rep("grey",6)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",9),"red", rep("grey",18),"blue","green","yellow",rep("grey",3)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",9),"red", rep("grey",21),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",10),"red", rep("grey",10),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",10),"red", rep("grey",13),"blue","green","yellow",rep("grey",7)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",10),"red", rep("grey",16),"blue","green","yellow",rep("grey",4)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",10),"red", rep("grey",19),"blue","green","yellow",rep("grey",1)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",10),"red", rep("grey",22),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",11),"red", rep("grey",9),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",11),"red", rep("grey",12),"blue","green","yellow",rep("grey",7)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",11),"red", rep("grey",15),"blue","green","yellow",rep("grey",4)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",11),"red", rep("grey",18),"blue","green","yellow",rep("grey",1)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",11),"red", rep("grey",21),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",12),"red", rep("grey",8),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",12),"red", rep("grey",11),"blue","green","yellow",rep("grey",7)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",12),"red", rep("grey",14),"blue","green","yellow",rep("grey",4)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",12),"red", rep("grey",17),"blue","green","yellow",rep("grey",3)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",12),"red", rep("grey",20),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",13),"red", rep("grey",7),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",13),"red", rep("grey",10),"blue","green","yellow",rep("grey",7)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",13),"red", rep("grey",13),"blue","green","yellow",rep("grey",4)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",13),"red", rep("grey",16),"blue","green","yellow",rep("grey",1)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",13),"red", rep("grey",19),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",14),"red", rep("grey",6),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",14),"red", rep("grey",9),"blue","green","yellow",rep("grey",13)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",14),"red", rep("grey",12),"blue","green","yellow",rep("grey",4)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",14),"red", rep("grey",15),"blue","green","yellow",rep("grey",1)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",14),"red", rep("grey",18),"blue","green","yellow",rep("grey",0)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",15),"red", rep("grey",5),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",15),"red", rep("grey",8),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",15),"red", rep("grey",11),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",15),"red", rep("grey",14),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",15),"red", rep("grey",17),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",16),"red", rep("grey",4),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",16),"red", rep("grey",7),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",16),"red", rep("grey",10),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",16),"red", rep("grey",13),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",16),"red", rep("grey",16),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",17),"red", rep("grey",3),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",17),"red", rep("grey",6),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",17),"red", rep("grey",9),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",17),"red", rep("grey",12),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",17),"red", rep("grey",15),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",18),"red", rep("grey",2),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",18),"red", rep("grey",5),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",18),"red", rep("grey",8),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",18),"red", rep("grey",11),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",18),"red", rep("grey",14),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",19),"red", rep("grey",1),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",19),"red", rep("grey",4),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",19),"red", rep("grey",7),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",19),"red", rep("grey",10),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",19),"red", rep("grey",13),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",20),"red", rep("grey",0),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",20),"red", rep("grey",3),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",20),"red", rep("grey",6),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",20),"red", rep("grey",9),"blue","green","yellow",rep("grey",10)))
DimPlot(Chondro_Fibro_CF, reduction = "umap", cols = c(rep("grey",20),"red", rep("grey",12),"blue","green","yellow",rep("grey",10)))
```
Return to C vs C, F vs F, and C/F vs C/F plots to compile C/F/C-F annotations
```{r}
comparison_1 <- subset(x = combined, idents = c("C-1_E16", "C-1_E18"))
DimPlot(comparison_1, reduction = "umap", cols = c("red", "blue"))
comparison_2 <- subset(x = combined, idents = c("C-2_E16", "C-5_E18"))
DimPlot(comparison_2, reduction = "umap", cols = c("red", "blue"))
comparison_3 <- subset(x = combined, idents = c("C-4_E18", "C-5_E16"))
DimPlot(comparison_3, reduction = "umap", cols = c("red", "blue"))
comparison_4 <- subset(x = combined, idents = c("C-2_E18", "C-3_E16"))
comparison_5 <- subset(x = combined, idents = c("C-2_E18", "C-3_E18"))
comparison_6 <- subset(x = combined, idents = c("C-3_E16", "C-3_E18"))
DimPlot(comparison_4, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_5, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_6, reduction = "umap", cols = c("red", "blue"))
comparison_7 <- subset(x = combined, idents = c("F-4_P0", "F-5_E16"))
DimPlot(comparison_7, reduction = "umap", cols = c("red", "blue"))
comparison_8 <- subset(x = combined, idents = c("F-1_E16", "F-5_P0"))
comparison_9 <- subset(x = combined, idents = c("F-1_E16", "F-1_E18"))
DimPlot(comparison_8, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_9, reduction = "umap", cols = c("red", "blue"))
comparison_10 <- subset(x = combined, idents = c("F-1_E18", "F-3_P0"))
comparison_11 <- subset(x = combined, idents = c("F-1_E18", "F-5_P0"))
DimPlot(comparison_10, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_11, reduction = "umap", cols = c("red", "blue"))
comparison_12 <- subset(x = combined, idents = c("F-1_P0", "F-2_E18"))
comparison_13 <- subset(x = combined, idents = c("F-1_P0", "F-3_E16"))
DimPlot(comparison_12, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_13, reduction = "umap", cols = c("red", "blue"))
comparison_14 <- subset(x = combined, idents = c("F-2_E18", "F-3_E16"))
comparison_15 <- subset(x = combined, idents = c("F-2_E18", "F-6_E16"))
DimPlot(comparison_14, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_15, reduction = "umap", cols = c("red", "blue"))
comparison_16 <- subset(x = combined, idents = c("F-3_E16", "F-5_P0"))
comparison_17 <- subset(x = combined, idents = c("F-3_E16", "F-6_E16"))
DimPlot(comparison_16, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_17, reduction = "umap", cols = c("red", "blue"))
comparison_18 <- subset(x = combined, idents = c("F-2_E18", "F-5_P0"))
DimPlot(comparison_18, reduction = "umap", cols = c("red", "blue"))
comparison_19 <- subset(x = combined, idents = c("C/F-1_E18", "C/F-5_P0"))
DimPlot(comparison_19, reduction = "umap", cols = c("red", "blue"))
comparison_20 <- subset(x = combined, idents = c("C/F-2_E18", "C/F-2_P0"))
comparison_21 <- subset(x = combined, idents = c("C/F-2_E18", "C/F-3_P0"))
comparison_22 <- subset(x = combined, idents = c("C/F-2_E18", "C/F-4_P0"))
DimPlot(comparison_20, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_21, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_22, reduction = "umap", cols = c("red", "blue"))
comparison_22 <- subset(x = combined, idents = c("C/F-2_P0", "C/F-3_E18"))
comparison_23 <- subset(x = combined, idents = c("C/F-2_P0", "C/F-4_E18"))
DimPlot(comparison_22, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_23, reduction = "umap", cols = c("red", "blue"))
comparison_24 <- subset(x = combined, idents = c("C/F-3_E18", "C/F-6_P0"))
comparison_25 <- subset(x = combined, idents = c("C/F-3_E18", "C/F-7_P0"))
DimPlot(comparison_24, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_25, reduction = "umap", cols = c("red", "blue"))
comparison_26 <- subset(x = combined, idents = c("C/F-6_P0", "C/F-7_P0"))
DimPlot(comparison_26, reduction = "umap", cols = c("red", "blue"))
comparison_27 <- subset(x = combined, idents = c("C/F-1_E18", "C-2_E16"))
comparison_28 <- subset(x = combined, idents = c("C/F-1_P0", "C-2_E18"))
comparison_29 <- subset(x = combined, idents = c("C/F-1_P0", "C-3_E16"))
comparison_30 <- subset(x = combined, idents = c("C/F-1_P0", "C-3_E18"))
comparison_31 <- subset(x = combined, idents = c("C/F-1_P0", "C-4_E16"))
DimPlot(comparison_27, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_28, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_29, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_30, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_31, reduction = "umap", cols = c("red", "blue"))
comparison_32 <- subset(x = combined, idents = c("C/F-2_E18", "C-1_E16"))
comparison_33 <- subset(x = combined, idents = c("C/F-2_E18", "C-1_E18"))
comparison_34 <- subset(x = combined, idents = c("C/F-2_E18", "C-3_E16"))
comparison_35 <- subset(x = combined, idents = c("C/F-2_P0", "C-1_E16"))
comparison_36 <- subset(x = combined, idents = c("C/F-2_P0", "C-1_E18"))
comparison_37 <- subset(x = combined, idents = c("C/F-2_P0", "C-2_E16"))
comparison_38 <- subset(x = combined, idents = c("C/F-2_P0", "C-3_E16"))
DimPlot(comparison_32, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_33, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_34, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_35, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_36, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_37, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_38, reduction = "umap", cols = c("red", "blue"))
comparison_39 <- subset(x = combined, idents = c("C/F-3_E18", "C-2_E16"))
comparison_40 <- subset(x = combined, idents = c("C/F-3_E18", "C-5_E18"))
comparison_41 <- subset(x = combined, idents = c("C/F-4_E18", "C-1_E16"))
comparison_42 <- subset(x = combined, idents = c("C/F-4_E18", "C-1_E18"))
comparison_43 <- subset(x = combined, idents = c("C/F-4_E18", "C-4_E16"))
DimPlot(comparison_39, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_40, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_41, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_42, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_43, reduction = "umap", cols = c("red", "blue"))
comparison_44 <- subset(x = combined, idents = c("C/F-4_P0", "C-2_E16"))
comparison_45 <- subset(x = combined, idents = c("C/F-5_P0", "C-2_E16"))
comparison_46 <- subset(x = combined, idents = c("C/F-6_P0", "C-2_E16"))
comparison_47 <- subset(x = combined, idents = c("C/F-7_P0", "C-2_E16"))
comparison_48 <- subset(x = combined, idents = c("C/F-6_P0", "C-5_E18"))
comparison_49 <- subset(x = combined, idents = c("C/F-7_P0", "C-5_E18"))
DimPlot(comparison_44, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_45, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_46, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_47, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_48, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_49, reduction = "umap", cols = c("red", "blue"))
comparison_50 <- subset(x = combined, idents = c("F-1_P0", "C-2_E16"))
comparison_51 <- subset(x = combined, idents = c("F-2_P0", "C-1_E16"))
comparison_52 <- subset(x = combined, idents = c("F-2_P0", "C-1_E18"))
comparison_53 <- subset(x = combined, idents = c("F-2_P0", "C-2_E18"))
comparison_54 <- subset(x = combined, idents = c("F-2_P0", "C-3_E16"))
comparison_55 <- subset(x = combined, idents = c("F-2_P0", "C-3_E18"))
comparison_56 <- subset(x = combined, idents = c("F-2_P0", "C-4_E16"))
comparison_57 <- subset(x = combined, idents = c("F-2_P0", "C-4_E18"))
comparison_58 <- subset(x = combined, idents = c("F-2_P0", "C-5_E16"))
DimPlot(comparison_50, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_51, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_52, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_53, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_54, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_55, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_56, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_57, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_58, reduction = "umap", cols = c("red", "blue"))
comparison_59 <- subset(x = combined, idents = c("C/F-1_E18", "F-1_P0"))
comparison_60 <- subset(x = combined, idents = c("C/F-1_E18", "F-2_E16"))
comparison_61 <- subset(x = combined, idents = c("C/F-1_E18", "F-2_E18"))
comparison_62 <- subset(x = combined, idents = c("C/F-1_E18", "F-4_P0"))
comparison_63 <- subset(x = combined, idents = c("C/F-1_E18", "F-5_E16"))
comparison_64 <- subset(x = combined, idents = c("C/F-1_E18", "F-5_P0"))
comparison_65 <- subset(x = combined, idents = c("F-2_E16", "C/F-5_P0"))
comparison_66 <- subset(x = combined, idents = c("F-2_P0", "C/F-1_P0"))
comparison_67 <- subset(x = combined, idents = c("F-2_P0", "C/F-2_P0"))
comparison_68 <- subset(x = combined, idents = c("F-2_P0", "C/F-4_E18"))
DimPlot(comparison_59, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_60, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_61, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_62, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_63, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_64, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_65, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_66, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_67, reduction = "umap", cols = c("red", "blue"))
DimPlot(comparison_68, reduction = "umap", cols = c("red", "blue"))
```
Combine the endothelium
```{r}
Endothelium <- subset(x = combined, idents = c("AECs_ADULT", "ECs_E16", "ECs_E18", "ECs_P0", "SECs_ADULT"))
DimPlot(Endothelium, reduction = "umap")
Endo_subset1 <- subset(x = Endothelium, idents = c("AECs_ADULT", "ECs_E16"))
Endo_subset2 <- subset(x = Endothelium, idents = c("AECs_ADULT", "ECs_E18"))
Endo_subset3 <- subset(x = Endothelium, idents = c("AECs_ADULT", "ECs_P0"))
Endo_subset4 <- subset(x = Endothelium, idents = c("ECs_E16", "ECs_E18"))
Endo_subset5 <- subset(x = Endothelium, idents = c("ECs_E16", "ECs_P0"))
Endo_subset6 <- subset(x = Endothelium, idents = c("ECs_E16", "SECs_ADULT"))
Endo_subset7 <- subset(x = Endothelium, idents = c("ECs_E18", "ECs_P0"))
Endo_subset8 <- subset(x = Endothelium, idents = c("ECs_E18", "SECs_ADULT"))
Endo_subset9 <- subset(x = Endothelium, idents = c("ECs_P0", "SECs_ADULT"))
DimPlot(Endo_subset1, reduction = "umap")
DimPlot(Endo_subset2, reduction = "umap")
DimPlot(Endo_subset3, reduction = "umap")
DimPlot(Endo_subset4, reduction = "umap")
DimPlot(Endo_subset5, reduction = "umap")
DimPlot(Endo_subset6, reduction = "umap")
DimPlot(Endo_subset7, reduction = "umap")
DimPlot(Endo_subset8, reduction = "umap")
DimPlot(Endo_subset9, reduction = "umap")
```
Next, re-annotate the Pericytes (P) population
```{r}
Pericytes <- subset(x = combined, idents = c("P-1_ADULT", "P-1_E16", "P-1_E18", "P-1_P0", "P-2_ADULT","P-2_E16","P-2_E18","P-2_P0","P-3_ADULT"))
P_subset1 <- subset(x = Pericytes, idents = c("P-1_ADULT", "P-1_E16"))
P_subset2 <- subset(x = Pericytes, idents = c("P-1_ADULT", "P-1_E18"))
P_subset3 <- subset(x = Pericytes, idents = c("P-1_ADULT", "P-1_P0"))
P_subset4 <- subset(x = Pericytes, idents = c("P-1_ADULT", "P-2_ADULT"))
P_subset5 <- subset(x = Pericytes, idents = c("P-1_ADULT", "P-2_E16"))
P_subset6 <- subset(x = Pericytes, idents = c("P-1_ADULT", "P-2_E18"))
P_subset7 <- subset(x = Pericytes, idents = c("P-1_ADULT", "P-2_P0"))
P_subset8 <- subset(x = Pericytes, idents = c("P-1_ADULT", "P-3_ADULT"))
P_subset9 <- subset(x = Pericytes, idents = c("P-1_E16", "P-1_E18"))
P_subset10 <- subset(x = Pericytes, idents = c("P-1_E16", "P-1_P0"))
P_subset11 <- subset(x = Pericytes, idents = c("P-1_E16", "P-2_ADULT"))
P_subset12 <- subset(x = Pericytes, idents = c("P-1_E16", "P-2_E16"))
P_subset13 <- subset(x = Pericytes, idents = c("P-1_E16", "P-2_E18"))
P_subset14 <- subset(x = Pericytes, idents = c("P-1_E16", "P-2_P0"))
P_subset15 <- subset(x = Pericytes, idents = c("P-1_E16", "P-3_ADULT"))
P_subset16 <- subset(x = Pericytes, idents = c("P-1_E18", "P-1_P0"))
P_subset17 <- subset(x = Pericytes, idents = c("P-1_E18", "P-2_ADULT"))
P_subset18 <- subset(x = Pericytes, idents = c("P-1_E18", "P-2_E16"))
P_subset19 <- subset(x = Pericytes, idents = c("P-1_E18", "P-2_E18"))
P_subset20 <- subset(x = Pericytes, idents = c("P-1_E18", "P-2_P0"))
P_subset21 <- subset(x = Pericytes, idents = c("P-1_E18", "P-3_ADULT"))
P_subset22 <- subset(x = Pericytes, idents = c("P-1_P0", "P-2_ADULT"))
P_subset23 <- subset(x = Pericytes, idents = c("P-1_P0", "P-2_E16"))
P_subset24 <- subset(x = Pericytes, idents = c("P-1_P0", "P-2_E18"))
P_subset25 <- subset(x = Pericytes, idents = c("P-1_P0", "P-2_P0"))
P_subset26 <- subset(x = Pericytes, idents = c("P-1_P0", "P-3_ADULT"))
P_subset27 <- subset(x = Pericytes, idents = c("P-2_ADULT", "P-2_E16"))
P_subset28 <- subset(x = Pericytes, idents = c("P-2_ADULT", "P-2_E18"))
P_subset29 <- subset(x = Pericytes, idents = c("P-2_ADULT", "P-2_P0"))
P_subset30 <- subset(x = Pericytes, idents = c("P-2_ADULT", "P-3_ADULT"))
P_subset31 <- subset(x = Pericytes, idents = c("P-2_E16", "P-2_E18"))
P_subset32 <- subset(x = Pericytes, idents = c("P-2_E16", "P-2_P0"))
P_subset33 <- subset(x = Pericytes, idents = c("P-2_E16", "P-3_ADULT"))
P_subset34 <- subset(x = Pericytes, idents = c("P-2_E18", "P-2_P0"))
P_subset35 <- subset(x = Pericytes, idents = c("P-2_E18", "P-3_ADULT"))
P_subset36 <- subset(x = Pericytes, idents = c("P-2_P0", "P-3_ADULT"))
DimPlot(P_subset1, reduction = "umap")
DimPlot(P_subset2, reduction = "umap")
DimPlot(P_subset3, reduction = "umap")
DimPlot(P_subset4, reduction = "umap")
DimPlot(P_subset5, reduction = "umap")
DimPlot(P_subset6, reduction = "umap")
DimPlot(P_subset7, reduction = "umap")
DimPlot(P_subset8, reduction = "umap")
DimPlot(P_subset9, reduction = "umap")
DimPlot(P_subset10, reduction = "umap")
DimPlot(P_subset11, reduction = "umap")
DimPlot(P_subset12, reduction = "umap")
DimPlot(P_subset13, reduction = "umap")
DimPlot(P_subset14, reduction = "umap")
DimPlot(P_subset15, reduction = "umap")
DimPlot(P_subset16, reduction = "umap")
DimPlot(P_subset17, reduction = "umap")
DimPlot(P_subset18, reduction = "umap")
DimPlot(P_subset19, reduction = "umap")
DimPlot(P_subset20, reduction = "umap")
DimPlot(P_subset21, reduction = "umap")
DimPlot(P_subset22, reduction = "umap")
DimPlot(P_subset23, reduction = "umap") 
DimPlot(P_subset24, reduction = "umap")
DimPlot(P_subset25, reduction = "umap")
DimPlot(P_subset26, reduction = "umap")
DimPlot(P_subset27, reduction = "umap")
DimPlot(P_subset28, reduction = "umap")
DimPlot(P_subset29, reduction = "umap")
DimPlot(P_subset30, reduction = "umap")
DimPlot(P_subset31, reduction = "umap")
DimPlot(P_subset32, reduction = "umap")
DimPlot(P_subset33, reduction = "umap")
DimPlot(P_subset34, reduction = "umap")
DimPlot(P_subset35, reduction = "umap")
DimPlot(P_subset36, reduction = "umap")
```
Now do Schwann cells
```{r}
Schwann_Cells <- subset(x = combined, idents = c("Schwann_E16", "Schwann_E18", "Schwann_P0"))
DimPlot(Schwann_Cells, reduction = "umap")
```
Now do the undefined populations
```{r}
Undefined <- subset(x = combined, idents = c("UD-1_P0", "UD-2_P0", "UD-3_P0", "UD_E16"))
DimPlot(Undefined, reduction = "umap")
```
Stroma completed, now move to the Heme. First, create a combined Heme object with the annotations from each library:
```{r}
load("C:/Users/thall/Desktop/Hall et al. CSC/singlecell2/HemeAdult/HemeADULT_regress2.Robj")
load("C:/Users/thall/Desktop/Hall et al. CSC/singlecell2/HemeE16/HemeE16_regress2.Robj")
load("C:/Users/thall/Desktop/Hall et al. CSC/singlecell2/HemeE18/HemeE18_regress2.Robj")
load("C:/Users/thall/Desktop/Hall et al. CSC/singlecell2/HemeP0/HemeP0_regress2.Robj")
```
Add developmental time to identities
```{r}
Idents(HemeE16_regress) <- paste(Idents(HemeE16_regress), "E16", sep="_")
Idents(HemeE18_regress) <- paste(Idents(HemeE18_regress), "E18", sep="_")
Idents(HemeP0_regress) <- paste(Idents(HemeP0_regress), "P0", sep="_")
Idents(HemeADULT_regress) <- paste(Idents(HemeADULT_regress), "ADULT", sep="_")
```
Check that identities include developmental time
```{r}
summary(Idents(HemeE16_regress))
summary(Idents(HemeE18_regress))
summary(Idents(HemeP0_regress))
summary(Idents(HemeADULT_regress))
```
Combine Objects
```{r}
combinedHeme <- merge(x = HemeE16_regress, y = list(HemeE18_regress,HemeP0_regress,HemeADULT_regress), add.cell.ids = c("HemeE16","HemeE18", "HemeP0", "HemeADULT"))
tail(x = combinedHeme@meta.data)
summary(Idents(combinedHeme))
table(combinedHeme@meta.data$Time)
DefaultAssay(combinedHeme) <- "RNA"
combinedHeme <- FindVariableFeatures(combinedHeme, selection.method = "vst", nfeatures = 2000)
top10 <- head(VariableFeatures(combinedHeme), 10)
top10
all.genes <- rownames(combinedHeme)
combinedHeme <- ScaleData(combinedHeme, features = all.genes)
combinedHeme <- RunPCA(combinedHeme, features = VariableFeatures(object = combinedHeme))
ElbowPlot(combinedHeme)
combinedHeme <- RunUMAP(combinedHeme, dims = 1:20)
DimPlot(combinedHeme, reduction = "umap")
save(combinedHeme, file = "C:/Users/thall/Desktop/singlecell2/Heme_combined.Robj")
```
If you ever return, just load the "Heme_combined.Robj" object. Go through all cluster combinations and identify overlapping populations. Start with the clusters I've annotated as "Bas".
```{r}
Basophils <- subset(x = combinedHeme, idents = c("Bas_E18", "Bas_P0"))
DimPlot(Basophils, reduction = "umap")
```
B cells
```{r}
Bcells <- subset(x = combinedHeme, idents = c("BCell_E16",  "BCell_E18", "Bcell1_ADULT", "Bcell1_P0", "Bcell2_ADULT", "BCell2_P0"))
Bcells_subset1 <- subset(x = combinedHeme, idents = c("BCell_E16",  "BCell_E18"))
Bcells_subset2 <- subset(x = combinedHeme, idents = c("BCell_E16", "Bcell1_ADULT"))
Bcells_subset3 <- subset(x = combinedHeme, idents = c("BCell_E16",  "Bcell1_P0"))
Bcells_subset4 <- subset(x = combinedHeme, idents = c("BCell_E16",  "Bcell2_ADULT"))
Bcells_subset5 <- subset(x = combinedHeme, idents = c("BCell_E16",  "BCell2_P0"))
Bcells_subset6 <- subset(x = combinedHeme, idents = c("BCell_E18", "Bcell1_ADULT"))
Bcells_subset7 <- subset(x = combinedHeme, idents = c("BCell_E18", "Bcell1_P0"))
Bcells_subset8 <- subset(x = combinedHeme, idents = c("BCell_E18", "Bcell2_ADULT"))
Bcells_subset9 <- subset(x = combinedHeme, idents = c("BCell_E18", "BCell2_P0"))
Bcells_subset10 <- subset(x = combinedHeme, idents = c("Bcell1_ADULT", "Bcell1_P0"))
Bcells_subset11 <- subset(x = combinedHeme, idents = c("Bcell1_ADULT", "Bcell2_ADULT"))
Bcells_subset12 <- subset(x = combinedHeme, idents = c("Bcell1_ADULT", "BCell2_P0"))
Bcells_subset13 <- subset(x = combinedHeme, idents = c("Bcell1_P0", "Bcell2_ADULT"))
Bcells_subset14 <- subset(x = combinedHeme, idents = c("Bcell1_P0", "BCell2_P0"))
Bcells_subset15 <- subset(x = combinedHeme, idents = c("Bcell2_ADULT", "BCell2_P0"))
DimPlot(Bcells_subset1, reduction = "umap")
DimPlot(Bcells_subset2, reduction = "umap")
DimPlot(Bcells_subset3, reduction = "umap")
DimPlot(Bcells_subset4, reduction = "umap")
DimPlot(Bcells_subset5, reduction = "umap")
DimPlot(Bcells_subset6, reduction = "umap")
DimPlot(Bcells_subset7, reduction = "umap")
DimPlot(Bcells_subset8, reduction = "umap")
DimPlot(Bcells_subset9, reduction = "umap")
DimPlot(Bcells_subset10, reduction = "umap")
DimPlot(Bcells_subset11, reduction = "umap")
DimPlot(Bcells_subset12, reduction = "umap")
DimPlot(Bcells_subset13, reduction = "umap")
DimPlot(Bcells_subset14, reduction = "umap")
DimPlot(Bcells_subset15, reduction = "umap")
```
Dendritic Cells
```{r}
Dendritic <- subset(x = combinedHeme, idents = c("DC_E16",  "DC_E18", "DC_P0"))
DimPlot(Dendritic, reduction = "umap")
```
Eos/Bas populations
```{r}
Eos_Bas <- subset(x = combinedHeme, idents = c("Eos/Bas_ADULT",  "Eos/Bas_E18", "Eos/Bas_P0","EosP/BasP_E16", "EosP_P0"))
Eos_Bas_subset1 <- subset(x = Eos_Bas, idents = c("Eos/Bas_ADULT",  "Eos/Bas_E18"))
Eos_Bas_subset2 <- subset(x = Eos_Bas, idents = c("Eos/Bas_ADULT",  "Eos/Bas_P0"))
Eos_Bas_subset3 <- subset(x = Eos_Bas, idents = c("Eos/Bas_ADULT",  "EosP/BasP_E16"))
Eos_Bas_subset4 <- subset(x = Eos_Bas, idents = c("Eos/Bas_ADULT",  "EosP_P0"))
Eos_Bas_subset5 <- subset(x = Eos_Bas, idents = c("Eos/Bas_E18", "Eos/Bas_P0"))
Eos_Bas_subset6 <- subset(x = Eos_Bas, idents = c("Eos/Bas_E18", "EosP/BasP_E16"))
Eos_Bas_subset7 <- subset(x = Eos_Bas, idents = c("Eos/Bas_E18", "EosP_P0"))
Eos_Bas_subset8 <- subset(x = Eos_Bas, idents = c("Eos/Bas_P0", "EosP/BasP_E16"))
Eos_Bas_subset9 <- subset(x = Eos_Bas, idents = c("Eos/Bas_P0", "EosP_P0"))
Eos_Bas_subset10 <- subset(x = Eos_Bas, idents = c("EosP/BasP_E16", "EosP_P0"))
DimPlot(Eos_Bas_subset1, reduction = "umap")
DimPlot(Eos_Bas_subset2, reduction = "umap")
DimPlot(Eos_Bas_subset3, reduction = "umap")
DimPlot(Eos_Bas_subset4, reduction = "umap")
DimPlot(Eos_Bas_subset5, reduction = "umap")
DimPlot(Eos_Bas_subset, reduction = "umap")
DimPlot(Eos_Bas_subset6, reduction = "umap")
DimPlot(Eos_Bas_subset7, reduction = "umap")
DimPlot(Eos_Bas_subset8, reduction = "umap")
DimPlot(Eos_Bas_subset9, reduction = "umap")
DimPlot(Eos_Bas_subset10, reduction = "umap")
```
EryP
```{r}
EryProg <- subset(x = combinedHeme, idents = c("EryP_ADULT", "EryP_P0"))
DimPlot(EryProg, reduction = "umap")
```
HSPCs
```{r}
HSPCs <- subset(x = combinedHeme, idents = c("HSPC_ADULT", "HSPC_E16", "HSPC_E18", "HSPC1_P0", "HSPC2_P0", "HSPC3_P0"))
HSPC_subset1 <- subset(x = HSPCs, idents = c("HSPC_ADULT", "HSPC_E16"))
HSPC_subset2 <- subset(x = HSPCs, idents = c("HSPC_ADULT", "HSPC_E18"))
HSPC_subset3 <- subset(x = HSPCs, idents = c("HSPC_ADULT", "HSPC1_P0"))
HSPC_subset4 <- subset(x = HSPCs, idents = c("HSPC_ADULT", "HSPC2_P0"))
HSPC_subset5 <- subset(x = HSPCs, idents = c("HSPC_ADULT", "HSPC3_P0"))
HSPC_subset6 <- subset(x = HSPCs, idents = c("HSPC_E16", "HSPC_E18"))
HSPC_subset7 <- subset(x = HSPCs, idents = c("HSPC_E16", "HSPC1_P0"))
HSPC_subset8 <- subset(x = HSPCs, idents = c("HSPC_E16", "HSPC2_P0"))
HSPC_subset9 <- subset(x = HSPCs, idents = c("HSPC_E16", "HSPC3_P0"))
HSPC_subset10 <- subset(x = HSPCs, idents = c("HSPC_E18", "HSPC1_P0"))
HSPC_subset11 <- subset(x = HSPCs, idents = c("HSPC_E18", "HSPC2_P0"))
HSPC_subset12 <- subset(x = HSPCs, idents = c("HSPC_E18", "HSPC3_P0"))
HSPC_subset13 <- subset(x = HSPCs, idents = c("HSPC1_P0", "HSPC2_P0"))
HSPC_subset14 <- subset(x = HSPCs, idents = c("HSPC1_P0", "HSPC3_P0"))
HSPC_subset15 <- subset(x = HSPCs, idents = c("HSPC2_P0", "HSPC3_P0"))
DimPlot(HSPC_subset1, reduction = "umap")
DimPlot(HSPC_subset2, reduction = "umap")
DimPlot(HSPC_subset3, reduction = "umap")
DimPlot(HSPC_subset4, reduction = "umap")
DimPlot(HSPC_subset5, reduction = "umap")
DimPlot(HSPC_subset6, reduction = "umap")
DimPlot(HSPC_subset7, reduction = "umap")
DimPlot(HSPC_subset8, reduction = "umap")
DimPlot(HSPC_subset9, reduction = "umap")
DimPlot(HSPC_subset10, reduction = "umap")
DimPlot(HSPC_subset11, reduction = "umap")
DimPlot(HSPC_subset12, reduction = "umap")
DimPlot(HSPC_subset13, reduction = "umap")
DimPlot(HSPC_subset14, reduction = "umap")
DimPlot(HSPC_subset15, reduction = "umap")
```
Mast Cells
```{r}
MastCells <- subset(x = combinedHeme, idents = c("Mast1_ADULT", "Mast1_E16", "Mast1_E18", "Mast1_P0", "Mast2_ADULT", "Mast2_P0", "Mast3_E16"))
MastCells_subset1 <- subset(x = MastCells, idents = c("Mast1_ADULT", "Mast1_E16"))
MastCells_subset2 <- subset(x = MastCells, idents = c("Mast1_ADULT", "Mast1_E18"))
MastCells_subset3 <- subset(x = MastCells, idents = c("Mast1_ADULT", "Mast1_P0"))
MastCells_subset4 <- subset(x = MastCells, idents = c("Mast1_ADULT", "Mast2_ADULT"))
MastCells_subset5 <- subset(x = MastCells, idents = c("Mast1_ADULT", "Mast2_P0"))
MastCells_subset6 <- subset(x = MastCells, idents = c("Mast1_ADULT", "Mast3_E16"))
MastCells_subset7 <- subset(x = MastCells, idents = c("Mast1_E16", "Mast1_E18"))
MastCells_subset8 <- subset(x = MastCells, idents = c("Mast1_E16", "Mast1_P0"))
MastCells_subset9 <- subset(x = MastCells, idents = c("Mast1_E16", "Mast2_ADULT"))
MastCells_subset10 <- subset(x = MastCells, idents = c("Mast1_E16", "Mast2_P0"))
MastCells_subset11 <- subset(x = MastCells, idents = c("Mast1_E16", "Mast3_E16"))
MastCells_subset12 <- subset(x = MastCells, idents = c("Mast1_E18", "Mast1_P0"))
MastCells_subset13 <- subset(x = MastCells, idents = c("Mast1_E18", "Mast2_ADULT"))
MastCells_subset14 <- subset(x = MastCells, idents = c("Mast1_E18", "Mast2_P0"))
MastCells_subset15 <- subset(x = MastCells, idents = c("Mast1_E18", "Mast3_E16"))
MastCells_subset16 <- subset(x = MastCells, idents = c("Mast1_P0", "Mast2_ADULT"))
MastCells_subset17 <- subset(x = MastCells, idents = c("Mast1_P0", "Mast2_P0"))
MastCells_subset18 <- subset(x = MastCells, idents = c("Mast1_P0", "Mast3_E16"))
MastCells_subset19 <- subset(x = MastCells, idents = c("Mast2_ADULT", "Mast2_P0"))
MastCells_subset20 <- subset(x = MastCells, idents = c("Mast2_ADULT", "Mast3_E16"))
MastCells_subset21 <- subset(x = MastCells, idents = c("Mast2_P0", "Mast3_E16"))
MastCellsE16 <- subset(x = combinedHeme, idents = c("Mast1_ADULT", "Mast1_E16", "Mast1_E18", "Mast1_P0", "Mast2_ADULT", "Mast2_E16", "Mast2_P0", "Mast3_E16"))
MastCellsE16_subset1 <- subset(x = MastCellsE16, idents = c("Mast1_ADULT", "Mast2_E16"))
MastCellsE16_subset2 <- subset(x = MastCellsE16, idents = c("Mast1_E16", "Mast2_E16"))
MastCellsE16_subset3 <- subset(x = MastCellsE16, idents = c("Mast1_E18", "Mast2_E16"))
MastCellsE16_subset4 <- subset(x = MastCellsE16, idents = c("Mast1_P0", "Mast2_E16"))
MastCellsE16_subset5 <- subset(x = MastCellsE16, idents = c("Mast2_ADULT", "Mast2_E16"))
MastCellsE16_subset6 <- subset(x = MastCellsE16, idents = c("Mast2_E16", "Mast2_P0"))
MastCellsE16_subset7 <- subset(x = MastCellsE16, idents = c("Mast2_E16", "Mast3_E16"))
DimPlot(MastCellsE16_subset1, reduction = "umap")
DimPlot(MastCellsE16_subset2, reduction = "umap")
DimPlot(MastCellsE16_subset3, reduction = "umap")
DimPlot(MastCellsE16_subset4, reduction = "umap")
DimPlot(MastCellsE16_subset5, reduction = "umap")
DimPlot(MastCellsE16_subset6, reduction = "umap")
DimPlot(MastCellsE16_subset7, reduction = "umap")
```
MegP
```{r}
MegProg <- subset(x = combinedHeme, idents = c("MegP_ADULT", "MegP_P0"))
DimPlot(MegProg, reduction = "umap")
```
Monocytes
```{r}
Monocytes <- subset(x = combinedHeme, idents = c("Mono1_ADULT", "Mono1_E18", "Mono1_P0", "Mono2_ADULT", "Mono2_E18", "Mono2_P0", "Mono3_ADULT", "Mono3_E18", "Mono4_E18", "Mono5_E18", "Mono6_E18"))
Monocytes_subset1 <- subset(x = Monocytes, idents = c("Mono1_ADULT", "Mono1_E18"))
Monocytes_subset2 <- subset(x = Monocytes, idents = c("Mono1_ADULT", "Mono1_P0"))
Monocytes_subset3 <- subset(x = Monocytes, idents = c("Mono1_ADULT", "Mono2_ADULT"))
Monocytes_subset4 <- subset(x = Monocytes, idents = c("Mono1_ADULT", "Mono2_E18"))
Monocytes_subset5 <- subset(x = Monocytes, idents = c("Mono1_ADULT", "Mono2_P0"))
Monocytes_subset6 <- subset(x = Monocytes, idents = c("Mono1_ADULT", "Mono3_E18"))
Monocytes_subset7 <- subset(x = Monocytes, idents = c("Mono1_ADULT", "Mono4_E18"))
Monocytes_subset8 <- subset(x = Monocytes, idents = c("Mono1_ADULT", "Mono5_E18"))
Monocytes_subset9 <- subset(x = Monocytes, idents = c("Mono1_ADULT", "Mono6_E18"))
Monocytes_subset10 <- subset(x = Monocytes, idents = c("Mono1_E18", "Mono1_P0"))
Monocytes_subset11 <- subset(x = Monocytes, idents = c("Mono1_E18", "Mono2_ADULT"))
Monocytes_subset12 <- subset(x = Monocytes, idents = c("Mono1_E18", "Mono2_E18"))
Monocytes_subset13 <- subset(x = Monocytes, idents = c("Mono1_E18", "Mono2_P0"))
Monocytes_subset14 <- subset(x = Monocytes, idents = c("Mono1_E18", "Mono3_E18"))
Monocytes_subset15 <- subset(x = Monocytes, idents = c("Mono1_E18",  "Mono4_E18"))
Monocytes_subset16 <- subset(x = Monocytes, idents = c("Mono1_E18", "Mono5_E18"))
Monocytes_subset17 <- subset(x = Monocytes, idents = c("Mono1_E18", "Mono6_E18"))
Monocytes_subset18 <- subset(x = Monocytes, idents = c("Mono1_P0", "Mono2_ADULT"))
Monocytes_subset19 <- subset(x = Monocytes, idents = c("Mono1_P0", "Mono2_E18"))
Monocytes_subset20 <- subset(x = Monocytes, idents = c("Mono1_P0", "Mono2_P0"))
Monocytes_subset21 <- subset(x = Monocytes, idents = c("Mono1_P0", "Mono3_E18"))
Monocytes_subset22 <- subset(x = Monocytes, idents = c("Mono1_P0", "Mono4_E18"))
Monocytes_subset23 <- subset(x = Monocytes, idents = c("Mono1_P0",  "Mono5_E18"))
Monocytes_subset24 <- subset(x = Monocytes, idents = c("Mono1_P0", "Mono6_E18"))
Monocytes_subset25 <- subset(x = Monocytes, idents = c("Mono2_ADULT", "Mono2_E18"))
Monocytes_subset26 <- subset(x = Monocytes, idents = c("Mono2_ADULT", "Mono2_P0"))
Monocytes_subset27 <- subset(x = Monocytes, idents = c("Mono2_ADULT", "Mono3_E18"))
Monocytes_subset28 <- subset(x = Monocytes, idents = c("Mono2_ADULT", "Mono4_E18"))
Monocytes_subset29 <- subset(x = Monocytes, idents = c("Mono2_ADULT", "Mono5_E18"))
Monocytes_subset30 <- subset(x = Monocytes, idents = c("Mono2_ADULT", "Mono6_E18"))
Monocytes_subset31 <- subset(x = Monocytes, idents = c("Mono2_E18", "Mono2_P0"))
Monocytes_subset32 <- subset(x = Monocytes, idents = c("Mono2_E18", "Mono3_E18"))
Monocytes_subset33 <- subset(x = Monocytes, idents = c("Mono2_E18", "Mono4_E18"))
Monocytes_subset34 <- subset(x = Monocytes, idents = c("Mono2_E18", "Mono5_E18"))
Monocytes_subset35 <- subset(x = Monocytes, idents = c("Mono2_E18", "Mono6_E18"))
Monocytes_subset36 <- subset(x = Monocytes, idents = c("Mono2_P0", "Mono3_E18"))
Monocytes_subset37 <- subset(x = Monocytes, idents = c("Mono2_P0", "Mono4_E18"))
Monocytes_subset38 <- subset(x = Monocytes, idents = c("Mono2_P0", "Mono5_E18"))
Monocytes_subset39 <- subset(x = Monocytes, idents = c("Mono2_P0", "Mono6_E18"))
Monocytes_subset40 <- subset(x = Monocytes, idents = c("Mono3_E18", "Mono4_E18"))
Monocytes_subset41 <- subset(x = Monocytes, idents = c("Mono3_E18", "Mono5_E18"))
Monocytes_subset42 <- subset(x = Monocytes, idents = c("Mono3_E18", "Mono6_E18"))
Monocytes_subset43 <- subset(x = Monocytes, idents = c("Mono4_E18", "Mono5_E18"))
Monocytes_subset44 <- subset(x = Monocytes, idents = c("Mono4_E18", "Mono6_E18"))
Monocytes_subset45 <- subset(x = Monocytes, idents = c("Mono5_E18", "Mono6_E18"))
DimPlot(Monocytes_subset1, reduction = "umap")
DimPlot(Monocytes_subset2, reduction = "umap")
DimPlot(Monocytes_subset3, reduction = "umap")
DimPlot(Monocytes_subset4, reduction = "umap")
DimPlot(Monocytes_subset5, reduction = "umap")
DimPlot(Monocytes_subset6, reduction = "umap")
DimPlot(Monocytes_subset7, reduction = "umap")
DimPlot(Monocytes_subset8, reduction = "umap")
DimPlot(Monocytes_subset9, reduction = "umap")
DimPlot(Monocytes_subset10, reduction = "umap")
DimPlot(Monocytes_subset11, reduction = "umap")
DimPlot(Monocytes_subset12, reduction = "umap")
DimPlot(Monocytes_subset13, reduction = "umap")
DimPlot(Monocytes_subset14, reduction = "umap")
DimPlot(Monocytes_subset15, reduction = "umap")
DimPlot(Monocytes_subset16, reduction = "umap")
DimPlot(Monocytes_subset17, reduction = "umap")
DimPlot(Monocytes_subset18, reduction = "umap")
DimPlot(Monocytes_subset19, reduction = "umap")
DimPlot(Monocytes_subset20, reduction = "umap")
DimPlot(Monocytes_subset21, reduction = "umap")
DimPlot(Monocytes_subset22, reduction = "umap")
DimPlot(Monocytes_subset23, reduction = "umap")
DimPlot(Monocytes_subset24, reduction = "umap")
DimPlot(Monocytes_subset25, reduction = "umap")
DimPlot(Monocytes_subset26, reduction = "umap")
DimPlot(Monocytes_subset27, reduction = "umap")
DimPlot(Monocytes_subset28, reduction = "umap")
DimPlot(Monocytes_subset29, reduction = "umap")
DimPlot(Monocytes_subset30, reduction = "umap")
DimPlot(Monocytes_subset31, reduction = "umap")
DimPlot(Monocytes_subset32, reduction = "umap")
DimPlot(Monocytes_subset33, reduction = "umap")
DimPlot(Monocytes_subset34, reduction = "umap")
DimPlot(Monocytes_subset35, reduction = "umap")
DimPlot(Monocytes_subset36, reduction = "umap")
DimPlot(Monocytes_subset37, reduction = "umap")
DimPlot(Monocytes_subset38, reduction = "umap")
DimPlot(Monocytes_subset39, reduction = "umap")
DimPlot(Monocytes_subset40, reduction = "umap")
DimPlot(Monocytes_subset41, reduction = "umap")
DimPlot(Monocytes_subset42, reduction = "umap")
DimPlot(Monocytes_subset43, reduction = "umap")
DimPlot(Monocytes_subset44, reduction = "umap")
DimPlot(Monocytes_subset45, reduction = "umap")
Monocytes_subset46 <- subset(x = Monocytes, idents = c("Mono1_ADULT", "Mono3_ADULT"))
Monocytes_subset47 <- subset(x = Monocytes, idents = c("Mono1_E18", "Mono3_ADULT"))
Monocytes_subset48 <- subset(x = Monocytes, idents = c("Mono1_P0", "Mono3_ADULT"))
Monocytes_subset49 <- subset(x = Monocytes, idents = c("Mono2_ADULT", "Mono3_ADULT"))
Monocytes_subset50 <- subset(x = Monocytes, idents = c("Mono2_E18", "Mono3_ADULT"))
Monocytes_subset51 <- subset(x = Monocytes, idents = c("Mono2_P0", "Mono3_ADULT"))
Monocytes_subset52 <- subset(x = Monocytes, idents = c("Mono3_ADULT", "Mono3_E18"))
Monocytes_subset53 <- subset(x = Monocytes, idents = c("Mono3_ADULT", "Mono4_E18"))
Monocytes_subset54 <- subset(x = Monocytes, idents = c("Mono3_ADULT", "Mono5_E18"))
Monocytes_subset55 <- subset(x = Monocytes, idents = c("Mono3_ADULT", "Mono6_E18"))
DimPlot(Monocytes_subset46, reduction = "umap")
DimPlot(Monocytes_subset47, reduction = "umap")
DimPlot(Monocytes_subset48, reduction = "umap")
DimPlot(Monocytes_subset49, reduction = "umap")
DimPlot(Monocytes_subset50, reduction = "umap")
DimPlot(Monocytes_subset51, reduction = "umap")
DimPlot(Monocytes_subset52, reduction = "umap")
DimPlot(Monocytes_subset53, reduction = "umap")
DimPlot(Monocytes_subset54, reduction = "umap")
DimPlot(Monocytes_subset55, reduction = "umap")
```
MyP
```{r}
MyProg <- subset(x = combinedHeme, idents = c("MyP1_ADULT", "MyP1_E18", "MyP1_P0", "MyP2_ADULT", "MyP2_E18", "MyP2_P0"))
MyProg_subset1 <- subset(x = MyProg, idents = c("MyP1_ADULT", "MyP1_E18"))
MyProg_subset2 <- subset(x = MyProg, idents = c("MyP1_ADULT", "MyP1_P0"))
MyProg_subset3 <- subset(x = MyProg, idents = c("MyP1_ADULT", "MyP2_ADULT"))
MyProg_subset4 <- subset(x = MyProg, idents = c("MyP1_ADULT", "MyP2_E18"))
MyProg_subset5 <- subset(x = MyProg, idents = c("MyP1_ADULT", "MyP2_P0"))
MyProg_subset6 <- subset(x = MyProg, idents = c("MyP1_E18", "MyP1_P0"))
MyProg_subset7 <- subset(x = MyProg, idents = c("MyP1_E18", "MyP2_ADULT"))
MyProg_subset8 <- subset(x = MyProg, idents = c("MyP1_E18", "MyP2_E18"))
MyProg_subset9 <- subset(x = MyProg, idents = c("MyP1_E18", "MyP2_P0"))
MyProg_subset10 <- subset(x = MyProg, idents = c("MyP1_P0", "MyP2_ADULT"))
MyProg_subset11 <- subset(x = MyProg, idents = c("MyP1_P0", "MyP2_E18"))
MyProg_subset12 <- subset(x = MyProg, idents = c("MyP1_P0", "MyP2_P0"))
MyProg_subset13 <- subset(x = MyProg, idents = c("MyP2_ADULT", "MyP2_E18"))
MyProg_subset14 <- subset(x = MyProg, idents = c("MyP2_ADULT", "MyP2_P0"))
MyProg_subset15 <- subset(x = MyProg, idents = c("MyP2_E18", "MyP2_P0"))
DimPlot(MyProg_subset1, reduction = "umap")
DimPlot(MyProg_subset2, reduction = "umap")
DimPlot(MyProg_subset3, reduction = "umap")
DimPlot(MyProg_subset4, reduction = "umap")
DimPlot(MyProg_subset5, reduction = "umap")
DimPlot(MyProg_subset6, reduction = "umap")
DimPlot(MyProg_subset7, reduction = "umap")
DimPlot(MyProg_subset8, reduction = "umap")
DimPlot(MyProg_subset9, reduction = "umap")
DimPlot(MyProg_subset10, reduction = "umap")
DimPlot(MyProg_subset11, reduction = "umap")
DimPlot(MyProg_subset12, reduction = "umap")
DimPlot(MyProg_subset13, reduction = "umap")
DimPlot(MyProg_subset14, reduction = "umap")
DimPlot(MyProg_subset15, reduction = "umap")
```
Neutrophils
```{r}
Neutrophils <- subset(x = combinedHeme, idents = c("Neu_ADULT", "Neu_E16", "Neu_E18", "Neu_P0"))
DimPlot(Neutrophils, reduction = "umap")
```
Undefined cells
```{r}
Undefined <- subset(x = combinedHeme, idents = c("UD1_E16", "UD1_E18", "UD2_E16", "UD2_E18"))
DimPlot(Undefined, reduction = "umap")
Undefined_subset1 <- subset(x = Undefined, idents = c("UD1_E16", "UD1_E18"))
Undefined_subset2 <- subset(x = Undefined, idents = c("UD1_E16", "UD2_E16"))
Undefined_subset3 <- subset(x = Undefined, idents = c("UD1_E16", "UD2_E18"))
Undefined_subset4 <- subset(x = Undefined, idents = c("UD1_E18", "UD2_E16"))
Undefined_subset5 <- subset(x = Undefined, idents = c("UD1_E18", "UD2_E18"))
Undefined_subset6 <- subset(x = Undefined, idents = c("UD2_E16", "UD2_E18"))
DimPlot(Undefined_subset1, reduction = "umap")
DimPlot(Undefined_subset2, reduction = "umap")
DimPlot(Undefined_subset3, reduction = "umap")
DimPlot(Undefined_subset4, reduction = "umap")
DimPlot(Undefined_subset5, reduction = "umap")
DimPlot(Undefined_subset6, reduction = "umap")
```
T Cells
```{r}
Tcells <- subset(x = combinedHeme, idents = c("TCell_E18", "TCell_P0", "TCell1_E16", "TCell2_E16", "TCell3_E16", "TCell4_E16", "TCell5_E16", "TCell6_E16"))
Tcells_subset1 <- subset(x = Tcells, idents = c("TCell_E18", "TCell_P0"))
Tcells_subset2 <- subset(x = Tcells, idents = c("TCell_E18", "TCell1_E16"))
Tcells_subset3<- subset(x = Tcells, idents = c("TCell_E18", "TCell2_E16"))
Tcells_subset4 <- subset(x = Tcells, idents = c("TCell_E18", "TCell3_E16"))
Tcells_subset5 <- subset(x = Tcells, idents = c("TCell_E18", "TCell4_E16"))
Tcells_subset6 <- subset(x = Tcells, idents = c("TCell_E18", "TCell5_E16"))
Tcells_subset7 <- subset(x = Tcells, idents = c("TCell_E18", "TCell6_E16"))
Tcells_subset8 <- subset(x = Tcells, idents = c("TCell_P0", "TCell1_E16"))
Tcells_subset9 <- subset(x = Tcells, idents = c("TCell_P0", "TCell2_E16"))
Tcells_subset10 <- subset(x = Tcells, idents = c("TCell_P0", "TCell3_E16"))
Tcells_subset11 <- subset(x = Tcells, idents = c("TCell_P0", "TCell4_E16"))
Tcells_subset12 <- subset(x = Tcells, idents = c("TCell_P0", "TCell5_E16"))
Tcells_subset13 <- subset(x = Tcells, idents = c("TCell_P0", "TCell6_E16"))
Tcells_subset14 <- subset(x = Tcells, idents = c("TCell1_E16", "TCell2_E16"))
Tcells_subset15 <- subset(x = Tcells, idents = c("TCell1_E16", "TCell3_E16"))
Tcells_subset16 <- subset(x = Tcells, idents = c("TCell1_E16", "TCell4_E16"))
Tcells_subset17 <- subset(x = Tcells, idents = c("TCell1_E16", "TCell5_E16"))
Tcells_subset18 <- subset(x = Tcells, idents = c("TCell1_E16", "TCell6_E16"))
Tcells_subset19 <- subset(x = Tcells, idents = c("TCell2_E16", "TCell3_E16"))
Tcells_subset20 <- subset(x = Tcells, idents = c("TCell2_E16", "TCell4_E16"))
Tcells_subset21 <- subset(x = Tcells, idents = c("TCell2_E16", "TCell5_E16"))
Tcells_subset22 <- subset(x = Tcells, idents = c("TCell2_E16", "TCell6_E16"))
Tcells_subset23 <- subset(x = Tcells, idents = c("TCell3_E16", "TCell4_E16"))
Tcells_subset24 <- subset(x = Tcells, idents = c("TCell3_E16", "TCell5_E16"))
Tcells_subset25 <- subset(x = Tcells, idents = c("TCell3_E16", "TCell6_E16"))
Tcells_subset26 <- subset(x = Tcells, idents = c("TCell4_E16", "TCell5_E16"))
Tcells_subset27 <- subset(x = Tcells, idents = c("TCell4_E16", "TCell6_E16"))
Tcells_subset28 <- subset(x = Tcells, idents = c("TCell5_E16", "TCell6_E16"))
DimPlot(Tcells_subset1, reduction = "umap")
DimPlot(Tcells_subset2, reduction = "umap")
DimPlot(Tcells_subset3, reduction = "umap")
DimPlot(Tcells_subset4, reduction = "umap")
DimPlot(Tcells_subset5, reduction = "umap")
DimPlot(Tcells_subset6, reduction = "umap")
DimPlot(Tcells_subset7, reduction = "umap")
DimPlot(Tcells_subset8, reduction = "umap")
DimPlot(Tcells_subset9, reduction = "umap")
DimPlot(Tcells_subset10, reduction = "umap")
DimPlot(Tcells_subset11, reduction = "umap")
DimPlot(Tcells_subset12, reduction = "umap")
DimPlot(Tcells_subset13, reduction = "umap")
DimPlot(Tcells_subset14, reduction = "umap")
DimPlot(Tcells_subset15, reduction = "umap")
DimPlot(Tcells_subset16, reduction = "umap")
DimPlot(Tcells_subset17, reduction = "umap")
DimPlot(Tcells_subset18, reduction = "umap")
DimPlot(Tcells_subset19, reduction = "umap")
DimPlot(Tcells_subset20, reduction = "umap")
DimPlot(Tcells_subset21, reduction = "umap")
DimPlot(Tcells_subset22, reduction = "umap")
DimPlot(Tcells_subset23, reduction = "umap")
DimPlot(Tcells_subset24, reduction = "umap")
DimPlot(Tcells_subset25, reduction = "umap")
DimPlot(Tcells_subset26, reduction = "umap")
DimPlot(Tcells_subset27, reduction = "umap")
DimPlot(Tcells_subset28, reduction = "umap")
```
Recolor all of the UMAP plots
```{r}
load("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Stroma/StromaE16_regress2")
load("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Stroma/StromaE18_regress2")
load("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Stroma/StromaP0_regress2")
load("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/Stroma/StromaADULT_regress2")
load("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/HemeAdult/HemeADULT_regress2")
load("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/HemeE16/HemeE16_regress2")
load("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/HemeE18/HemeE18_regress2")
load("C:/Users/thall/Desktop/Loaner Desktop/Hall et al. CSC/singlecell2/HemeP0/HemeP0_regress2")
DimPlot(StromaE16_regress2, reduction = "umap", cols = c(rep('purple',5), 'lightgreen',rep('lightblue',6),'blue','lightgreen','maroon','red'), pt.size = 1)
DimPlot(StromaE18_regress2, reduction = "umap", cols = c(rep('purple',5),'lightgreen','lightgreen',rep('lightblue',3),'pink','purple','purple','maroon','red'), pt.size = 1)
DimPlot(StromaP0_regress2, reduction = "umap", cols = c('lightgreen','lightgreen',rep('blue',3),'lightblue','purple',rep('lightblue',3),'purple','purple','pink','pink','lightblue','purple','purple','red','maroon'), pt.size = 1)
DimPlot(StromaADULT_regress2, reduction = "umap", cols = c(rep('purple',3), rep('lightblue',6),rep('lightgreen',3),'red','grey','navy','red'), pt.size = 1)
DimPlot(HemeADULT_regress, reduction = "umap", cols = c('navy','navy','purple',rep('grey',3),'pink','purple','lightgreen','lightgreen','pink','red','lightblue','lightblue','navy','navy','maroon','blue'),pt.size = 1)
DimPlot(HemeE16_regress, reduction = "umap", cols = c('navy','grey','pink','pink','red',rep('lightblue',3),rep('maroon',3),'lightgreen',rep('maroon',3),'blue','blue'),pt.size = 1)
DimPlot(HemeE18_regress, reduction = "umap",cols = c('navy','grey','pink',rep('grey',4),'pink','pink','red','blue','blue','lightblue','maroon','lightgreen','lightgreen','purple','grey','lightblue'),pt.size = 1)
DimPlot(HemeP0_regress, reduction = "umap",cols = c('pink','purple','grey','pink','lightgreen','lightgreen','purple','pink','red','red','lightblue','lightblue','maroon','red','red','navy','grey','grey','pink','navy'),pt.size = 1)
```
